### 2022-12-14 draft.tex
Deploying to gh-pages from @ FrancisBanville/ms_maxent_networks@5714511bbb7c5379a9a4f4146d00f8a17640f682 🚀

For each network in our complete dataset, we estimated their
configuration of maximum entropy given each of these constraints. For
both types of heuristic MaxEnt models, we used a simulated annealing
algorithm with \(4\) chains, \(2000\) steps and an initial temperature
of \(0.2\). For each food web, we first generated one random Boolean
matrix per chain while fixing the number of species. We also maintained
the total number of interactions (i.e.~the sum of all elements in the
matrix) in the type I MaxEnt model and the joint degree sequence
(i.e.~the rows and columns sums) in the type II MaxEnt model. These were
our initial configurations. Then, we swapped interactions sequentially
while maintaining the original connectance or joint degree sequence.
Configurations with a higher SVD entropy than the previous one in the
chain were always accepted, whereas they were accepted with a
probability conditional to a decreasing temperature when lower. The
final configuration with the highest SVD entropy among the four chains
constitute the estimated maximum entropy configuration of a food web
given the constraint used.

>>>>

For each network in our complete dataset, we estimated their
configuration of maximum entropy given each of these constraints. For
both types of heuristic MaxEnt models, we used a simulated annealing
algorithm with \(4\) chains, \(2000\) steps and an initial temperature
of \(0.2\). For each food web, we first generated one random Boolean
matrix per chain while fixing the number of species. We also maintained
the total number of interactions (i.e.~the sum of all elements in the
matrix) in the type I MaxEnt model and the joint degree sequence
(i.e.~the rows and columns sums) in the type II MaxEnt model. These were
our initial configurations. Then, we swapped interactions sequentially
while maintaining the original connectance or joint degree sequence.
Configurations with a higher SVD entropy than the previous one in the
chain were always accepted, whereas they were accepted with a
probability conditional to a decreasing temperature and the difference
in SVD entropy when lower. The final configuration with the highest SVD
entropy among the four chains constitute the estimated maximum entropy
configuration of a food web given the constraint used.
